Carbonate chemistry at Ny-Ålesund

### 2023-05-31 awipev-CO2.Rmd
refined new chunk

>>>>

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# we calculate the duration of each stop

# Function written by Robert Schlegel
depth_time <- function(df){
  # Get proto event info
  ex1 <- rle(as.numeric(df$depth_group))
  ind1 <- rep(seq_along(ex1$lengths), ex1$lengths)
  s1 <- base::split(base::seq_len(nrow(df)), ind1)
  # Extract the start and end times per depth group
  depth_count <- do.call(rbind, lapply(s1, function(x)
    data.frame(depth_group = tmp$depth_group[min(x)],
               time_start = tmp$datetime[min(x)], 
               time_end = tmp$datetime[max(x)])))
  # Calculate the time spent there in seconds
  depth_count$time_spent <- depth_count$time_end-depth_count$time_start+3600
  # Convert to hours if desired
  depth_count$hours_spent <- as.numeric(depth_count$time_spent)/3600
  # Exit
  return(depth_count)
}

# First create the tibble
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
tmp <- d_all %>% 
  dplyr::select(datetime, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))

count_depth <- depth_time(tmp) 
plot_all_depths <- count_depth %>% 
  ggplot() +
  geom_bar(aes(x=hours_spent))
plot_all_depths
```
